**Measuring Depression and Anxiety with 4 items? Adaptation of the PHQ-4 to increase its Sensitivity to Subclinical Variability**

### 2024-12-10 paper/4_WIP/manuscript.qmd
minor todo

Moreover, Bayesian *t*-tests comparing the BDI-II scores between the refined and the original version at each integer score (0, 1, 2, 3) yielded no evidence in favour of a significant difference (BF > 3). In other words, having the same score on the refined version as on the original version was related to the same outcome on the BDI-II.

>>>>

Moreover, Bayesian *t*-tests (using *BayesFactor*'s `ttestBF()` function with default priors; **ADD REF TO PKG**) comparing the BDI-II scores between the refined and the original version at each integer score (0, 1, 2, 3) yielded no evidence in favour of a significant difference (BF > 3). In other words, having the same score on the refined version as on the original version was related to the same outcome on the BDI-II.
